Forecasting the 2024 U.S. Presidential Election: A Poll-of-Polls Approach for Predicting the Outcome

### 2024-11-04 paper/paper.qmd
debug reference

We use the statistical programming language R [@citeR] to analyze polling data from FiveThirtyEight’s U.S. Presidential election polls [@fivethirtyeight2024]. The dataset contains information such as pollster, polling date, methodology, sample size, state, and candidate support percentages. It allows us to track voter sentiment across different regions and polling methods, providing a comprehensive view of the election landscape. Additionally, irrelevant or incomplete entries were removed to ensure clean, high-quality data, and we retained only key variables to streamline the analysis. This careful selection and cleaning process ensure that the dataset offers a precise and representative snapshot of the election landscape.

@@

-   "pollster" represents the polling organization, modeled as a random effect to account for differences in reliability or bias between pollsters.

@@

The model fitting was performed using the `rstanarm` package, which allows for Bayesian inference using Markov Chain Monte Carlo (MCMC) methods. Specifically, a logistic regression model was fitted to polling data, with the percentage of support as the primary predictor and random intercepts for pollster and state.

@@

The model fit was evaluated using posterior predictive checks and residual diagnostics. The Bayesian logistic regression was fit with priors centered at 0.5, reflecting uncertainty in the initial estimates.

>>>>

We use the statistical programming language R [@citeR] to analyze polling data from FiveThirtyEight’s U.S. Presidential election polls [@FiveThirtyEight2024]. The dataset contains information such as pollster, polling date, methodology, sample size, state, and candidate support percentages. It allows us to track voter sentiment across different regions and polling methods, providing a comprehensive view of the election landscape. Additionally, irrelevant or incomplete entries were removed to ensure clean, high-quality data, and we retained only key variables to streamline the analysis. This careful selection and cleaning process ensure that the dataset offers a precise and representative snapshot of the election landscape.

@@

-   "pollster" represents the polling organization, modeled as a random effect to account for differences in reliability or bias between pollsters[@keyfitz1951sampling].

@@

The model fitting was performed using the `rstanarm`[@rstanarm] package, which allows for Bayesian inference using Markov Chain Monte Carlo (MCMC) methods. Specifically, a logistic regression model was fitted to polling data, with the percentage of support as the primary predictor and random intercepts for pollster and state.

@@

The model fit was evaluated using posterior predictive checks [@broom] and residual diagnostics. The Bayesian logistic regression was fit with priors centered at 0.5, reflecting uncertainty in the initial estimates.
